|

### 2025-02-21 output/seminar-slideshow.qmd
Apply canonical markdown

::: columns
::: column
![Un cubo rojo en perspectiva isométrica](../www/slideshow-assets/isometric-cube.jpg){fig-align="center"}
:::

@@

---@ackerman_multidimensional_2005-1 [p. 16]
:::
:::

@@

::::::: columns
::: column
```{r item-oblique-axes-3}
#| fig-align:  center
#| fig-height: 8
#| fig-width:  8
mirt_item <- tribble(
  ~item, ~a_1, ~a_2, ~d,
  1,     1,    1,    0
)

@@

::::: column
::: fragment
$$
  \mathbf{a}_1 = \begin{bmatrix}
    1 \\
    1
  \end{bmatrix};\quad
  d_1 = 0
$$
:::

@@

::: fragment
$$
  \begin{align}
    MDISC_1 &= \sqrt{
        [1, 1]
        \begin{bmatrix}
          1 \\
          1
        \end{bmatrix}
      } \\
      &= \sqrt{ 1 · 1 + 1 · 1 } \\
      &= \sqrt{ 1 + 1 } \\
      &= \sqrt{ 2 } \approx 1.41
  \end{align}
$$
:::
:::::
:::::::

@@

::: r-center
![Ítems de "ACT Mathematics Usage Test"](../www/Fig_1-6_Contemporary_Psychometrics.png){fig-align="center" height=400px}
:::

>>>>

::::: columns
::: column
![Un cubo rojo en perspectiva isométrica](../www/slideshow-assets/isometric-cube.jpg){fig-align="center"}
:::

@@

---@ackerman_multidimensional_2005-1 [p. 16]
:::
:::::

@@

:::::::: columns
::: column
```{r item-oblique-axes-3}
#| fig-align:  center
#| fig-height: 8
#| fig-width:  8
mirt_item <- tribble(
  ~item, ~a_1, ~a_2, ~d,
  1,     1,    1,    0
)

@@

:::::: column
::: fragment
$$
  \mathbf{a}_1 = \begin{bmatrix}
    1 \\
    1
  \end{bmatrix};\quad
  d_1 = 0
$$
:::

@@

::: fragment
$$
  \begin{align}
    MDISC_1 &= \sqrt{
        [1, 1]
        \begin{bmatrix}
          1 \\
          1
        \end{bmatrix}
      } \\
      &= \sqrt{ 1 · 1 + 1 · 1 } \\
      &= \sqrt{ 1 + 1 } \\
      &= \sqrt{ 2 } \approx 1.41
  \end{align}
$$
:::
::::::
::::::::

@@

::: r-center
![Ítems de "ACT Mathematics Usage Test"](../www/Fig_1-6_Contemporary_Psychometrics.png){fig-align="center" height="400px"}
:::
